Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{B}}$.} Sort the set of y-coordinates defined by all the segments of $H$ and $V$. Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $V_\ell$ of segments in $V$ that intersect with $\ell$. Let $S_\ell$ be the set of x-coordinates of the segments in $V_\ell$; we store $S_\ell$ in a binary search tree (BST) $\T$. Specifically, when $\ell$ hits the lower  (resp., upper) endpoint of a vertical segment $v = x \times [y_1, y_2]$ of $V$, we insert (resp., delete) the value $x$ into (resp., from) $\T$, which can be done in $O(\log n)$ amortized time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $H$, search $\T$ to determine if the successor $x'$ of $x_1$ in $S_\ell$. If $x' \le x_2$, then we output a pair $(h, p)$, where $p$ is the point $(x', y)$; otherwise, output nothing for $h$. The overall running time is $O(n \log n)$.

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$.} Sort the set of y-coordinates defined by all the segments in $H$ and all the rectangles in $R$. Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a structure $\T$ of \cite{aak+12}. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ with {\em weight} $x_2$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $P$, search $\T$ to determine the maximum weight $w$ of all the intervals in $S_\ell$ containing the value $x_1$. If $w \ne -\infty$, we output $(h, p)$ where the point $p$ is defined in a way depending on $w$: if $w \le x_2$, then $p = (w, y)$; otherwise $p = (x_2, y)$. The overall running time is $O(n \log n)$.

@@

Next, we aim to produce, for each pair $(h, r) \in H \times r$ such that $h$ crosses $r$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.

>>>>

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{B}}$.} Sort the set of y-coordinates defined by all the segments of $H$ and $V$. Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $V_\ell$ of segments in $V$ that intersect with $\ell$. Let $S_\ell$ be the set of x-coordinates of the segments in $V_\ell$; we store $S_\ell$ in a binary search tree (BST) $\T$. Specifically, when $\ell$ hits the lower  (resp., upper) endpoint of a vertical segment $v = x \times [y_1, y_2]$ of $V$, we insert (resp., delete) the value $x$ into (resp., from) $\T$, which can be done in $O(\log n)$ amortized time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $H$, search $\T$ to determine the successor $x'$ of $x_1$ in $S_\ell$. If $x' \le x_2$, then we output a pair $(h, p)$, where $p$ is the point $(x', y)$; otherwise, output nothing for $h$. The overall running time is $O(n \log n)$.

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$.} Sort the set of y-coordinates defined by all the segments in $H$ and all the rectangles in $R$. Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a stabbing-max structure $\T$ of \cite{aak+12}. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ with {\em weight} $x_2$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $P$, search $\T$ to determine the maximum weight $w$ of all the intervals in $S_\ell$ containing the value $x_1$. If $w \ne -\infty$, we output $(h, p)$ where the point $p$ is defined in a way depending on $w$: if $w \le x_2$, then $p = (w, y)$; otherwise $p = (x_2, y)$. The overall running time is $O(n \log n)$.

@@

Next, we aim to produce, for each pair $(h, r) \in H \times r$ such that $h$ crosses $r$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $H$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.
